An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-31 VLDB2026/main.tex
Update main.tex

	\textcolor{violet}{To investigate the time and space overhead of different algorithms,} we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}. Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512. \textcolor{red}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other 6 medium-scale datasets. Notably, the VBASE and PASE algorithms only support single-threaded construction.}

@@

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}. Although the third-ranked algorithm differs, we consider the ranking order remains stable since the performance of the third and fourth algorithms is comparable. So our findings remain consistent with those reported in Section 4.2.4. For brevity and due to space limitations, we omit further discussion of these redundant results.}
%	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}. Compared with the original server's experimental results (Figure \ref{fig:exp_8_2}($e$)), the conclusions remain identical to those described in Section 4.2.4. Due to space constraints, these details are not reiterated here.}

@@

\textcolor{red}{
Faiss, Milvus and VBASE effectively handle complex filtering by employing versatile "pre-filtering" or "post-filtering" strategies, granting them significant flexibility and broad applicability. This flexibility, however, is often counterbalanced by their relatively modest overall search performance. Relatively speaking, PASE performs less well across various aspects.}

>>>>

	\textcolor{violet}{To investigate the time and space overhead of different algorithms,} we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}. Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512. \textcolor{red}{We use 64 threads to build the index for the large-scale Deep100M dataset, and 32 threads for the other six datasets. Notably, the VBASE and PASE algorithms only support single-threaded construction.}

@@

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
	\textcolor{cyan}{Consistent with Section 4.2.4, we conduct additional range filtering experiments on the YT-Audio-Real dataset using the same server configuration, with results presented in Figure~\ref{fig:range-cross-platform}. Although the third-ranked algorithm differs, we consider the ranking order remains stable since the performance of the third and fourth algorithms is comparable. So our findings remain consistent with those reported in Section 4.2.3. For brevity and due to space limitations, we omit further discussion of these redundant results.}
%	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}. Compared with the original server's experimental results (Figure \ref{fig:exp_8_2}($e$)), the conclusions remain identical to those described in Section 4.2.4. Due to space constraints, these details are not reiterated here.}

@@

\textcolor{orange}{
Faiss, Milvus and VBASE effectively handle complex filtering by employing versatile "pre-filtering" or "post-filtering" strategies, granting them significant flexibility and broad applicability. This flexibility, however, is often counterbalanced by their relatively modest overall search performance. Relatively speaking, PASE performs less well across various aspects.}
